\documentclass[sigconf, authorversion]{acmartreview}

\usepackage{booktabs} % For formal tables
\usepackage[acronyms, nogroupskip, nonumberlist, nopostdot]{glossaries}
\makeglossaries
\usepackage{IEEEtrantools}
\usepackage{xargs}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage[inline,shortlabels]{enumitem}
\usepackage[binary-units=true]{siunitx}
\usepackage{subcaption}
\usepackage{url}
\usepackage{xcolor}

% TODO notes
\usepackage{todonotes}
 \presetkeys{todonotes}{inline, backgroundcolor=green, linecolor=black}{}
\newcommand{\michael}[1]{\todo[backgroundcolor=green]{Michael: #1}}
\newcommand{\paul}[1]{\todo[backgroundcolor=yellow]{Paul: #1}}
\newenvironment*{modifiedparagraph}{}{}
\newcommand{\modifiedtext}[1]{#1}

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\settopmatter{printacmref=false, printccs=false, printfolios=true}

\hyphenation{post-proces-sing}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}


\begin{document}
\title{GRASP-based Gate-Control List Synthesis for IEEE~Time-Sensitive Networks (TSN)}

\author{Michael L. Raagaard and Paul Pop}
\affiliation{%
  \institution{Technical University of Denmark}
  \city{Kongens Lyngby}
  \country{Denmark}
}
\email{michael@raagaard.dk,\quad paupo@dtu.dk}

\author{Silviu S. Craciunas}
\affiliation{%
  \institution{TTTech Computertechnik AG}
  \city{Vienna} 
  \country{Austria} 
}
\email{scr@tttech.com}

\begin{abstract}
\gls{tsn} is an IEEE effort to bring deterministic real-time capabilities to \IEEE{802.3 Ethernet}. \gls{tsn} meets the bandwidth and dependability requirements of emerging mixed-criticality applications, while ensuring timeliness of time-critical communication. The \IEEE{802.1Qbv} sub-standard introduces time-aware gates within network devices enabling fully deterministic temporal behavior of real-time communication. For each egress port, a \gls{gcl} specifies which queue (traffic class) may transmit at which points in time. Using this functionality enables frames to be forwarded in the network in a time-triggered manner.
In this paper, we are interested in synthesizing schedule tables for periodic time-critical flows on \gls{tsn} architectures such that timeliness is guaranteed, i.e., an assignment of critical Ethernet frames to egress port queues, and a construction of \glsplural{gcl} ensuring that all frames are schedulable.
The problem is formulated as a multi-objective combinatorial optimization problem, which minimizes the queue utilization as well as end-to-end latency.
We propose a scalable \gls{grasp}-based metaheuristic to solve this problem. The proposed approach is evaluated on synthetic and realistic test cases, and compared to results from related work.
\end{abstract}

%% MACROS 
\newcommand{\IEEE}[1]{\textit{IEEE #1}}
\newcommand{\mus}[1]{\SI{#1}{\micro\second}}
\renewcommand{\ms}[1]{\SI{#1}{\milli\second}}
\renewcommandx{\l}[1][1={v_a,v_b}]{\ensuremath{\left[#1 \right]}}
\newcommandx{\f}[3][1={i,m}, 2={\l}, 3=f]{\ensuremath{#3_{#1}^{#2}}}
\renewcommandx{\s}[3][1={i}, 2={}, 3=s]{\ensuremath{#3_{#1}^{#2}}}
\newcommand{\Kappa}{\mathrm{K}}
\newcommand{\lbound}[1]{\ensuremath{\underline{#1}}}
\newcommand{\ubound}[1]{\ensuremath{\overline{#1}}}

%autoref
\renewcommand*{\figureautorefname}{Fig.}
\renewcommand*{\sectionautorefname}{Sect.}
\renewcommand*{\subsectionautorefname}{Sect.}
\renewcommand*{\subsubsectionautorefname}{Sect.}
\renewcommand*{\equationautorefname}{Eq.}
\renewcommand*{\tableautorefname}{Table}
\newcommand{\algorithmautorefname}{Alg.}

\setlength{\abovecaptionskip}{0.5ex}
\setlength{\belowcaptionskip}{0.3ex}
%\setlength{\floatsep}{10ex}
\setlength{\textfloatsep}{2ex}
%\setlength{\bibsep}{0ex}
%\setlength{\partopsep}{0.3ex}

% glossary
\input{abbreviations}                                   
\input{notations}

\maketitle
\input{introduction.tex}
\input{architecture.tex}
\input{application.tex}
\input{tsn.tex}
\input{problem.tex}
\input{grasp.tex}
\input{evaluation.tex}
\input{conclusions.tex}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc}

\end{document}
